Bow shocks, bow waves, and dust waves

### 2019-02-02 papers/Papers1234/sigma-ori-arcs.tex
Write more on sigma Ori and start AE Aur paper

\title
% {No radiation supported dust wave around \(\sigma\) Orionis}
% OR
{Is the dusty bow shock around \(\sigma\) Orionis driven by an enclosed proplyd?}

@@

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
\begin{abstract}
  We critically evaluate the role of radiation and hydrodynamics in
  providing internal support for the bow-shaped infrared arc around
  the massive triple star system \(\sigma\)~Ori Aa/Ab/B in the IC434 \hii{}
  region.  We present evidence for hydrogen recombination line
  emission from the arc, which demonstrates that it cannot be a dust
  wave in which the grains have separated from the gas, as has been
  previously claimed.  On the other hand, we show that the fraction of
  the stellar luminosity trapped by the arc is insufficient for it to
  be supported by radiation if the grains and gas are well coupled.
  Therefore, the arc must be supported by the ram pressure of an
  internal wind.  However, the stellar wind from the OB stars in the
  \(\sigma\)~Ori Aa/Ab/B system are too weak by more than an order of
  magnitude.  We propose instead that it is the photoevaporated disk
  wind from the enclosed proplyd IRS~1B that provides the ram pressure
  support for the bow.
\end{abstract}

@@

\input{sec-dust-case-studies}
\bibliographystyle{mnras}
\bibliography{bowshocks-biblio}

>>>>

\title
% {No radiation supported dust wave around \(\sigma\) Orionis}
% OR
{\boldmath A dusty bow shock around \(\sigma\) Orionis driven by an enclosed proplyd?}

@@

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
\begin{abstract}
  We critically evaluate the role of radiation and hydrodynamics in
  providing internal support for the bow-shaped infrared arc around
  the massive triple star system \(\sigma\)~Ori Aa/Ab/B in the IC434 \hii{}
  region.  We present evidence for hydrogen recombination line
  emission from the arc, which demonstrates that it cannot be a
  decoupled dust wave, as has previously been claimed.  On the other
  hand, we show that the fraction of the stellar luminosity trapped by
  the arc is insufficient for it to be supported by radiation if the
  grains and gas are well coupled.  Therefore, the arc must be
  supported by the ram pressure of an internal wind.  However, the
  stellar winds from the OB stars in the \(\sigma\)~Ori Aa/Ab/B system seem
  too weak to provide this support on their own.  We propose instead
  that it is the photoevaporated disk wind from the enclosed proplyd
  IRS~1B that dominates the ram pressure support for the bow.
\end{abstract}

@@

\section{Why the inner arc cannot be a decoupled dust wave}
\label{sec:why-not-dust}

\section{Why the inner arc cannot be radiation-supported}
\label{sec:why-not-radiation}

SEDs of the two arcs

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/sigma-ori-comparison}
  \caption{Optical and infrared images of $\sigma$~Ori}
  \label{fig:sig-ori}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/sigma-ori-eastwest-cuts}
  \caption{Brightness profiles through $\sigma$~Ori inner arc.}
  \label{fig:sig-ori-cuts}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/sigma-ori-inner-outer}
  \caption{Combined mid-infrared and far-infrared views of the inner and outer arcs around $\sigma$~Ori}
  \label{fig:sig-ori-outer}
\end{figure}

\begin{figure}
  \centering
  \caption{Spectral energy distributions of arcs around $\sigma$~Ori}
  \label{fig:sig-ori-SED}
\end{figure}

\section{Weak stellar winds from the massive triple Aa/Ab/B}
\label{sec:stellar-winds-AB}

\section{Photoevaporation flow from the proplyd IRS~1B}
\label{sec:phot-flow-from}

\section{The nature of the outer dust arc}

\section{Conclusions}
\label{sec:conclusions}

\bibliographystyle{mnras}
\bibliography{bowshocks-biblio}
